%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

\documentclass[a4paper,11pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[top=1.4cm,bottom=0.8cm,left=1.2cm,right=1.2cm]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\hyphenpenalty=10000
\exhyphenpenalty=10000
\newcolumntype{C}{>{\centering\arraybackslash}X}
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{6pt}
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}
\usepackage{fontawesome5}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------
\noindent\begin{tabularx}{\linewidth}{@{} X @{}}
\Huge{Shilpa Gupta} \\[7.5pt]
\href{https://myportfolio-d378f.firebaseapp.com/}{\raisebox{-0.05\height}{\faLink} Shilpa.Portfolio} \ $|$ \
\href{https://github.com/Shilpa2504}{\raisebox{-0.05\height}{\faGithub} Shilpa2504} \ $|$ \
\href{https://www.linkedin.com/in/shilpa-gupta-621a90259/}{\raisebox{-0.05\height}{\faLinkedin} Shilpa Gupta} \\
\href{https://leetcode.com/Shilpa_gupta/}{\raisebox{-0.05\height} Leetcode} \ $|$ \
\href{mailto:shilpakalwar25@gmail.com}{\raisebox{-0.05\height} shilpakalwar25@gmail.com} \ $|$ \
\href{tel:7338683445}{\raisebox{-0.05\height} 7338683445}
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Accenture -- Packaged App Development Associate (PADA)} & Nov 2024 -- Present \\[2pt]
\multicolumn{2}{@{}X@{}}{$\bullet$ 1+ year experience developing enterprise Angular (17+) web applications on the MyISP platform.} \\
\multicolumn{2}{@{}X@{}}{$\bullet$ Implemented Micro Frontend (MFE) architecture, RxJS-based data flows, pagination, and NgRx state management using reusable UI components.} \\
\multicolumn{2}{@{}X@{}}{$\bullet$ Migrated applications to Angular 17+, improving performance, scalability, and maintainability by 25\%.} \\
\multicolumn{2}{@{}X@{}}{$\bullet$ Integrated REST APIs, handled CRUD operations, and worked in Agile/Scrum teams.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{FindInbox -- Web Developer Intern} & Nov 2023 -- Jan 2024 \\[2pt]
\multicolumn{2}{@{}X@{}}{{\small\bfseries A startup focused on educational technology solutions}} \\
\multicolumn{2}{@{}X@{}}{$\bullet$ Developed React.js web application using functional components, hooks, and component-based architecture.} \\
\multicolumn{2}{@{}X@{}}{$\bullet$ Integrated REST APIs and implemented state management for student assessment data.} \\
\multicolumn{2}{@{}X@{}}{$\bullet$ Built performance analytics features, improving UI responsiveness and usability by 20\%.} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

\begin{tabularx}{\linewidth}{@{}X@{}}
\textbf{StudyMate.ai -- AI-Powered Study Assistant (React.js, Node.js, MongoDB, AI APIs)} \ $|$ \
\href{https://github.com/Shilpa2504}{ GitHub} \ $|$ \
\href{https://study-mate-ai-six.vercel.app/login}{ Live} \\[2pt]
{$\bullet$ Built an AI-powered study companion enabling users to upload PDFs, ask context-aware questions, and generate quizzes using AI APIs.} \\
{$\bullet$ Developed interactive quiz generation and analytics dashboard to track learning progress and performance metrics.} \\
{$\bullet$ Implemented secure user authentication, session management, and responsive UI using React.js and component-based architecture.} \\
{$\bullet$ Integrated REST APIs and MongoDB for efficient document storage, user data, and quiz result management.} \\
{$\bullet$ Deployed on Vercel with optimized build pipeline, achieving fast load times and high availability.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{PizzeriaApp -- MEAN Stack (Angular, MongoDB, Express.js, Node.js)} \ $|$ \
\href{https://github.com/Shilpa2504/Pizzeria}{ GitHub} \ $|$ \
\href{https://pizzeria-ashen-alpha.vercel.app/}{ Live} \\[2pt]
\multicolumn{2}{@{}X@{}}{$\bullet$ Developed full-stack MEAN web application with dynamic pizza customization, cart management, and order tracking.} \\
\multicolumn{2}{@{}X@{}}{$\bullet$ Implemented REST APIs and CRUD operations to manage orders, users, and menu data.} \\
\multicolumn{2}{@{}X@{}}{$\bullet$ Designed responsive Angular components using component-based architecture and reusable services.} \\
\multicolumn{2}{@{}X@{}}{$\bullet$ Integrated MongoDB Atlas, improving data consistency and order processing efficiency by 20\%.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{}X@{}}
\textbf{NewsApp -- React.js, HTML, CSS, Bootstrap} \ $|$ \
\href{https://github.com/Shilpa2504/Newsapp.git}{ Newsapp.git} \\[2pt]
{$\bullet$ Developed React.js web application using component-based and class-based components.} \\
{$\bullet$ Integrated REST APIs (News API) to fetch, manage, and render real-time news data.} \\
{$\bullet$ Implemented state handling and category-based routing, improving user engagement by 20\%.} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}X@{}}
\textbf{Frontend:} Angular (17+), React.js, JavaScript (ES6+), HTML5, CSS3, Bootstrap \\
\textbf{Backend \& Databases:} Node.js, Express.js, REST APIs, CRUD, MongoDB, MySQL \\
\textbf{AI \& Tools:} AI API Integration, PDF Processing, Git, GitHub, npm, VS Code, Linux/Unix \\
\textbf{Concepts:} Micro Frontend (MFE), State Management, Pagination, Responsive Design, Agile/Scrum, Performance Optimization
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2020 - 2024 & BE in CSE at \textbf{Jss Academy of Technical Education, Bangalore} \hfill \normalsize (CGPA: 8.6) \\
2018 &      Class 12th  Assam Board \hfill  (74\%) \\
2016 &      Class 10th  Assam Board \hfill  (74\%) \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{Certification}
\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{$\bullet$ The Web Developer Bootcamp 2023 by Colt Steele} \hfill (2023) \\[3pt]
\textbf{$\bullet$ Microsoft GitHub Copilot Certification} \hfill (2024) \\[3pt]
\href{https://www.hackerrank.com/certificates/c703269ff0d5m}{$\bullet$ HackerRank Certifications: Data Structures (Basic)} \ $|$ \
\href{https://www.hackerrank.com/certificates/0b6cd38724b5/}{SQL}
\end{tabularx}

\vfill
\end{document}
